Coherent optical creation of a single molecule

### 2021-03-03 paper.tex
Reorder the discussion about other attempts

Molecular association of ultracold atoms takes advantage of the cooling and trapping techniques
that have been developed for atoms.
Associating atoms into deeply bound molecules is challenging
because of the small wavefunction overlap between the free-atom and molecular states
and the release of large binding energy.
A widely used method of overcoming these challenges is to associate atom pairs
into weakly bound molecules first,
and then transfer the molecules from this single internal state
to a desired rovibrational and electronic state,
releasing the binding energy by stimulated emission~\cite{Danzl2008, Ni2008, Lang2008,
  Takekoshi2014, Molony2014, Park2015, Guo2016, Kondov2019, Voges2020}.
So far, coherent molecular association has generally been achieved by magnetoassociation
through a magnetic Feshbach scattering resonance.
Optical transfer to these molecular state have also been demonstrated~\cite{Wynar2000,Rom2004}
but the transition is generally incoherent,
which limits their use to spectroscopic study of the molecular structure,
rather than creating and controlling the molecules.
Exceptions include Sr$_2$, where narrow-linewidth ($\sim 20~\mathrm{kHz}$) excited states
are available and optical association can be driven coherently~\cite{Stellmer2012,Reinaudi2012},
and $^{87}$Rb$^{85}$Rb with molecular states bound by only $1-2~\mathrm{MHz}$~\cite{He331}.
With these requirements, molecules involving non-magnetic atoms~\cite{PhysRevX.10.031037}
or atoms without narrow intercombination lines remain difficult to associate.

>>>>

Molecular association of ultracold atoms takes advantage of the cooling and trapping techniques
that have been developed for atoms.
Associating atoms into deeply bound molecules is challenging
because of the small wavefunction overlap between the free-atom and molecular states
and the release of large binding energy.
A widely used method of overcoming these challenges is to associate atom pairs
into weakly bound molecules first,
and then transfer the molecules from this single internal state
to a desired rovibrational and electronic state,
releasing the binding energy by stimulated emission~\cite{Danzl2008, Ni2008, Lang2008,
  Takekoshi2014, Molony2014, Park2015, Guo2016, Kondov2019, Voges2020}.
So far, coherent molecular association has generally been achieved by magnetoassociation
through a magnetic Feshbach scattering resonance.
Exceptions include Sr$_2$, where narrow-linewidth ($\sim 20~\mathrm{kHz}$) excited states
are available and optical association can be driven coherently~\cite{Stellmer2012,Reinaudi2012},
and $^{87}$Rb$^{85}$Rb with molecular states bound by only $1-2~\mathrm{MHz}$~\cite{He331}.
With these requirements, molecules involving non-magnetic atoms~\cite{PhysRevX.10.031037}
or atoms without narrow intercombination lines remain difficult to associate.
Optical association that can be applied to a wider range of molecule
have also been demonstrated~\cite{Wynar2000,Rom2004}
but the transition is generally incoherent,
which limits their use to spectroscopic study of the molecular structure,
rather than creating and controlling the molecules.
